Tutorial 2a

### 2025-07-06 Tutorial_2a.Rmd
update tutorial 2a (change figure)

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(point_interval="median_qi",.width=.95,alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,.7)) +
    labs(x = "time bin", y = "predicted hazard")

@@

```{r epred-pid-plot}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(point_interval="median_qi",
                    .width=.95,
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted hazard") +
   # ggtitle("Each participant (N = 6)") +
    facet_wrap(~pid, ncol=3)

>>>>

```{r epred-grand-plot}
 p1 <- ggplot(epreds_grand, aes(x=timebin, y=.epred, 
                          fill=prime, color=prime)) +
    stat_lineribbon(point_interval="median_qi",.width=c(.8,.95),alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,.7)) +
    labs(x = "time bin", y = "predicted hazard")

@@

```{r epred-pid-plot}
p2 <- ggplot(epreds_pid, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(point_interval="median_qi",
                    .width=c(.8,.95),
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(x = "time bin", y = "predicted hazard") +
   # ggtitle("Each participant (N = 6)") +
    facet_wrap(~pid, ncol=3)
